Structured Versus Decorated Cospans

### 2020-11-16 cospans.tex
Completed section 4 except for a question at the end.

\begin{thm} \label{thm:equiv}
Suppose $\ca{A}$ has finite colimits and $(F,\phi,\phi_0)\maps(\ca{A},+) \to (\bicat{Cat},\times,1)$ is a symmetric lax monoidal pseudofunctor that factors through $\bicat{Rex}$ as an ordinary pseudofunctor. 
Then the symmetric monoidal double category $F\lCsp$ of decorated cospans is equivalent to the symmetric monoidal double category $_L\lCsp(\inta F)$ of structured cospans, where $L \maps \A \to \inta F$ is the left adjoint of the induced Grothendieck opfibration $\U\maps \inta F \to \A$.
\end{thm}

@@

As noted for example by Shulman \cite{Shulman2010}, any double category $\lX$ gives rise to a bicategory $\bX$ in which:
\begin{itemize}
\item objects are objects of $\lX$,
\item morphisms are horizontal 1-cells of $\lX$,
\item 2-morphisms are \define{globular} 2-morphisms of $\lX$, meaning 2-morphisms whose source and target vertical 1-morphisms are identities,
\item composition of morphisms is given by horizontal composition of horizontal 1-cells in $\lX$,
\item vertical and horizontal composition of 2-morphisms are given by vertical and horizontal
composition of 2-morphisms in $\lX$.
\end{itemize}
Furthermore, any bicategory $\bX$ whatsoever gives rise to a category $\X$ in which:
\begin{itemize}
\item objects are objects of $\bX$,
\item morphisms are isomorphism classes of morphisms of $\bX$.   
\end{itemize}
Thus, the double category $F\lCsp$ of structured cospans constructed in \cref{thm:decorated_cospans} automatically gives rise to a bicategory, which we call $F\bCsp$, and a category, which we call $F\Csp$.

In \cref{DC} we gave conditions under which the double category $F\lCsp$ becomes symmetric
monoidal.   We would like the bicategory $F\bCsp$ and the category $F\Csp$ to become symmetric
monoidal under the same conditions, and indeed this is true.  Shulman \cite[Thm.\ 1.2]{Shulman2010} showed that when $\lX$ is `fibrant', any symmetrical monoidal structure on $\lX$ gives one on $\bX$.     We can apply this to decorated cospans as follows:

@@

\begin{proof}
Recall from \cref{defn:fibrant} that a double category is fibrant if every vertical 1-morphism has a `companion' and a `conjoint'.  Let $f \maps c \to c'$ be a vertical 1-morphism in $F\lCsp$. We can lift $f$ to a companion horizontal 1-cell $\hat{f}$:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$c$};
\node (B) at (1,0) {$c'$};
\node (C) at (2,0) {$c'$};
\node (D) at (1,-0.5) {$!_{c'} \in F(c')$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$f$} (B)
(C) edge node[above]{$1$} (B);
\end{tikzpicture}
\]
and then obtain the following two 2-morphisms:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0.5) {$c$};
\node (A') at (0,-0.5) {$c'$};
\node (B) at (1,0.5) {$c'$};
\node (C) at (2,0.5) {$c'$};
\node (C') at (2,-0.5) {$c'$};
\node (D) at (1,-0.5) {$c'$};
\node (E) at (3,0.5) {$!_{c'} \in F(c')$};
\node (F) at (3,-0.5) {$!_{c'} \in F(c')$};
\node (G) at (4,0.5) {$c$};
\node (H) at (5,0.5) {$c$};
\node (I) at (6,0.5) {$c$};
\node (G') at (4,-0.5) {$c$};
\node (H') at (5,-0.5) {$c'$};
\node (I') at (6,-0.5) {$c'$};
\node (J) at (7,0.5) {$!_{c} \in F(c)$};
\node (K) at (7,-0.5) {$!_{c'} \in F(c')$};
\node (L) at (1,-1) {$\tau_{1_{c'}} = 1_{!_{c'}}$};
\node (M) at (5,-1) {$\tau_f \maps F(f)(!_c) \to !_{c'}$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$f$} (B)
(C) edge node[above]{$1$} (B)
(A) edge node[left]{$f$} (A')
(C) edge node[left]{$1$} (C')
(A') edge node[above] {$1$} (D)
(C') edge node[above] {$1$} (D)
(B) edge node [left] {$1$} (D)
(G) edge node [above] {$1$} (H)
(G) edge node [left] {$1$} (G')
(H) edge node [left] {$f$} (H')
(G') edge node [above] {$f$} (H')
(I) edge node [above] {$1$} (H)
(I) edge node [left] {$f$} (I')
(I') edge node [above] {$1$} (H');
\end{tikzpicture}
\]
which satisfy the equations:
\[
\begin{tikzpicture}[scale=1.5]
\node (N) at (0,1.5) {$c$};
\node (O) at (1,1.5) {$c$};
\node (P) at (2,1.5) {$c$};
\node (Q) at (-1,1.5) {$!_c \in F(c)$};
\node (A) at (0,0.5) {$c$};
\node (A') at (0,-0.5) {$c'$};
\node (B) at (1,0.5) {$c'$};
\node (C) at (2,0.5) {$c'$};
\node (C') at (2,-0.5) {$c'$};
\node (D) at (1,-0.5) {$c'$};
\node (E) at (-1,0.5) {$!_{c'} \in F(c')$};
\node (F) at (-1,-0.5) {$!_{c'} \in F(c')$};
\node (G) at (4,1) {$c$};
\node (H) at (5,1) {$c$};
\node (I) at (6,1) {$c$};
\node (G') at (4,0) {$c'$};
\node (H') at (5,0) {$c'$};
\node (I') at (6,0) {$c'$};
\node (J) at (7,1) {$!_{c} \in F(c)$};
\node (K) at (7,0) {$!_{c'} \in F(c')$};
\node (Q) at (1,-1) {$\tau_f \maps F(f)(!_c) \to !_{c'}$};
\node (L) at (1,-1.5) {$\tau_{c'} = 1_{!_{c'}}$};
\node (M) at (5,-0.5) {$\tau_f \maps F(f)(!_c) \to !_{c'}$};
\node (R) at (3,0.5) {$=$};
\path[->,font=\scriptsize,>=angle 90]
(N) edge node[above]{$1$} (O)
(P) edge node[above]{$1$} (O)
(N) edge node[left]{$1$} (A)
(O) edge node[left]{$f$} (B)
(P) edge node[left]{$f$} (C)
(A) edge node[above]{$f$} (B)
(C) edge node[above]{$1$} (B)
(A) edge node[left]{$f$} (A')
(C) edge node[left]{$1$} (C')
(A') edge node[above] {$1$} (D)
(C') edge node[above] {$1$} (D)
(B) edge node [left] {$1$} (D)
(G) edge node [above] {$1$} (H)
(G) edge node [left] {$f$} (G')
(H) edge node [left] {$f$} (H')
(G') edge node [above] {$1$} (H')
(I) edge node [above] {$1$} (H)
(I) edge node [left] {$f$} (I')
(I') edge node [above] {$1$} (H');
\end{tikzpicture}
\]
\[
\begin{tikzpicture}[scale=1.5]
\node (G) at (-1,0.5) {$c$};
\node (H) at (-1,-0.5)  {$c'$};
\node (I) at (-2,0.5) {$c$};
\node (J) at (-2,-0.5) {$c$};
\node (A) at (0,0.5) {$c$};
\node (A') at (0,-0.5) {$c'$};
\node (B) at (1,0.5) {$c'$};
\node (C) at (2,0.5) {$c'$};
\node (C') at (2,-0.5) {$c'$};
\node (D) at (1,-0.5) {$c'$};
\node (E) at (1,1) {$!_{c'} \in F(c')$};
\node (F) at (1,-1) {$!_{c'} \in F(c')$};

@@

(A) edge node[above]{$f$} (B)
(C) edge node[above]{$1$} (B)
(A) edge node[left]{$f$} (A')
(C) edge node[left]{$1$} (C')
(A') edge node[above] {$1$} (D)
(C') edge node[above] {$1$} (D)
(B) edge node [left] {$1$} (D)
(A) edge node[above]{$1$} (G)
(G) edge node[left]{$f$} (H)
(A') edge node[above]{$1$} (H)
(J) edge node[above] {$f$} (H)
(I) edge node[left] {$1$} (J)
(I) edge node [above] {$1$} (G);
\end{tikzpicture}
\]
The right hand sides of the above two equations are given respectively by the 2-morphisms $U_f$ and $1_{\hat{f}}$. The conjoint of $f$ is given by the $F$-decorated cospan $\check{f}$ which is just the opposite of the companion above:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$c'$};
\node (B) at (1,0) {$c'$};
\node (C) at (2,0) {$c$};
\node (D) at (4,0) {$!_{c'} \in F(c')$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$1$} (B)
(C) edge node[above]{$f$} (B);
\end{tikzpicture}
\]
Just as $\hat{f}$ obeys the equations required of a companion, $\check{f}$ obeys the similar equations required of a conjoint.
\end{proof}

@@

This symmetric monoidal bicategory $F\Csp$ is a superior version of the symmetric monoidal bicategory $F$Cospan$(\A)$ constructed earlier by the second author \cite{Courser}, in that there is greater flexibility in the allowed 2-morphisms.

%The previous bicategory constructed by the second author suffered even more so from the issue discussed in the introduction. Given a symmetric lax monoidal functor $F \maps \mathrm{A} \to \mathrm{Set}$, a result of Fong \cite{Fong} yields a symmetric monoidal category $F \textnormal{Cospan}(\mathrm{A})$ which has:
%\begin{enumerate}
%\item{objects as those of $\mathrm{A}$ and}
%\item{morphisms as isomorphism classes of decorated cospans in $\mathrm{A}$.}
%\end{enumerate}
%The second author then using a result of Shulman \cite{Shul} extended this to a bicategory also called $F \textnormal{Cospan}(\mathrm{A})$ which has:
%\begin{enumerate}
%\item{objects as those of $\mathrm{A}$,}
%\item{morphisms as now just decorated cospans in $\mathrm{A}$, and}
%\item{2-morphisms as pairs of commuting diagrams:
%\[
%\begin{tikzpicture}[scale=1.5]
%\node (A) at (0,0) {$a$};
%\node (B) at (1,0.5) {$c$};
%\node (B') at (1,-0.5) {$c'$};
%\node (C) at (2,0) {$b$};
%\node (D) at (3,0) {$1$};
%\node (E) at (4,0.5) {$F(c)$};
%\node (E') at (4,-0.5) {$F(c')$};
%\path[->,font=\scriptsize,>=angle 90]
%(A) edge node[above]{$i$} (B)
%(C) edge node[above]{$o$} (B)
%(A) edge node[below]{$i'$} (B')
%(C) edge node[below]{$o'$} (B')
%(B) edge node [left] {$f$} (B')
%(D) edge node [above] {$d$} (E)
%(D) edge node [below] {$d'$} (E')
%(E) edge node [right] {$F(f)$} (E');
%\end{tikzpicture}
%\]
%}
%\end{enumerate}
%This was discussed in the introduction and it was mentioned how in the symmetric monoidal category version of $F \textnormal{Cospan}(\mathrm{A})$, that the two single-edged graphs:
%\[
%\begin{tikzpicture}[scale=1.5]
%\node (A) at (0,0) {$v_1$};
%\node (B) at (1,0) {$v_2$};
%\path[->,font=\scriptsize,>=angle 90]
%(A) edge node[above]{$e$} (B);
%\end{tikzpicture}
%\]
%and
%\[
%\begin{tikzpicture}[scale=1.5]
%\node (A) at (0,0) {$v_1$};
%\node (B) at (1,0) {$v_2.$};
%\path[->,font=\scriptsize,>=angle 90]
%(A) edge node[above]{$e'$} (B);
%\end{tikzpicture}
%\]
%resided in distinct isomorphism classes. In the bicategorical version of $F \textnormal{Cospan}(\mathrm{A})$ where we are no longer considering decorated cospans up to isomorphism class, there is no 2-morphism between these two graphs due to the strict commutativity of the triangle to the right above. This problem does not occur in the symmetric monoidal bicategory $H(\mathbb{F}\textnormal{Cospan}(\mathrm{A}))$ and there is in fact a 2-(iso)morphism between these two graphs given by the map $\tau \maps F(f)(d) \to d'$ which maps the edge $e$ to the edge $e'$, where $f$ is the underlying map of vertices.

%Again, let $F \maps \mathbf{FinSet} \to \mathbf{Set}$ be the symmetric lax monoidal functor that maps a finite set $N$ to the large set of all possible graph structures whose underlying set of vertices is $N$. Then a result of Fong \cite{Fong} yields a symmetric monoidal category $F\textnormal{Cospan}(\mathbf{FinSet})$ which has:
%\begin{enumerate}
%\item{finite sets as objects and}
%\item{isomorphism classes of `open' graphs as morphisms, where an open graph is a cospan of finite sets whose apex is equipped with the structure of a graph.}
%\end{enumerate}

%An example of an open graph is:
%\begin{center}
%\begin{tikzpicture}[scale=2.15]
%\node (N) at (0.5,-1.25) {$N=\{v_1,v_2,v_3\}$};
%    \node[circle,draw,inner sep=1pt,fill=gray,color=gray]         (x) at (-1.4,-.43) {};
%    \node at (-1.4,-.9) {$X$};
%    \node       (A) at (0,0) {$v_1$};
%    \node     (B) at (1,0) {$v_2$};
%    \node        (C) at (0.5,-.86) {$v_3$};
%    \node[circle,draw,inner sep=1pt,fill=gray,color=gray]         (y1) at (2.4,-.25) {};
%    \node[circle,draw,inner sep=1pt,fill=gray,color=gray]         (y2) at (2.4,-.61) {};
%    \node at (2.4,-.9) {$Y$};
%    \path (B) edge  [bend right,->-] node[above] {$e_1$} (A);
%    \path (A) edge  [bend right,->-] node[below] {$e_2$} (B);
%    \path (A) edge  [->-] node[left] {$e_3$} (C);
%    \path (C) edge  [->-] node[right] {$e_4$} (B);
%    \path[color=gray, very thick, shorten >=10pt, shorten <=5pt, ->, >=stealth] (x) edge (A);
%    \path[color=gray, very thick, shorten >=10pt, shorten <=5pt, ->, >=stealth] (y1) edge (B);
%    \path[color=gray, very thick, shorten >=10pt, shorten <=5pt, ->, >=stealth] (y2) edge (B);
%\end{tikzpicture}
%\end{center}
%Here, the sets $X$ and $Y$ serve as inputs and outputs. The second author then extended Fong's category using a result of Shulman \cite{Shul} to obtain a symmetric monoidal bicategory which has:

%the following two single-edged graphs constituted distinct isomorphism classes:
%\[
%\begin{tikzpicture}[scale=1.5]
%\node (A) at (0,0) {$v_1$};
%\node (B) at (2,0) {$v_2$};
%\node (C) at (0,-2) {$v_1$};
%\node (D) at (2,-2) {$v_2$};
%\path[->,font=\scriptsize,>=angle 90]
%(A) edge node[above]{$e$} (B)
%(C) edge node[above]{$e'$} (D);
%\end{tikzpicture}
%\]

We can then decategorify this symmetric monoidal bicategory to obtain a symmetric monoidal category generalizing the kind considered by Fong \cite{Fong}:

@@

In \cref{thm:equiv} we gave conditions under which the double category of \emph{decorated} cospans $F\lCsp$ is equivalent to the double category of \emph{structured} cospans ${}_L \lCsp(\int F)$.   We now show that under the same conditions we get an equivalence of bicategories and of
categories.

We have just seen in \cref{thm:bicat} that the decorated cospan
double category $F\lCsp$ gives rise to a bicategory $F\Csp$.   A similar result 
is known for structured cospan double categories \cite[Cor.\ 3.10]{BC}.  Namely, if $\A$ and $\X$ are categories with (chosen???) finite colimits and $L \maps \A \to \X$ preserves colimits, the 
the structured cospan double category ${}_L \lCsp(\X)$ is symmetric monoidal and cofibrant, so the resulting bicategory ${}_L \bCsp(\X)$ becomes symmetric monoidal as well.

Another result of Shulman \cite{Shulman2010} is the following:
\begin{lem}[Shulman, Prop.\ B.3]
An equivalence of fibrant double categories induces a biequivalence of horizontal bicategories.
\end{lem}

\begin{cor}
The bicategories $F\mathbf{Csp}$ and $H( {_L \lCsp(\X)})$ are biequivalent.
\end{cor}

>>>>

\begin{thm} \label{thm:equiv}
Suppose $\ca{A}$ has finite colimits and $(F,\phi,\phi_0)\maps(\ca{A},+) \to (\bicat{Cat},\times)$ is a symmetric lax monoidal pseudofunctor that factors through $\bicat{Rex}$ as an ordinary pseudofunctor.   Then the symmetric monoidal double category $F\lCsp$ of decorated cospans is equivalent to the symmetric monoidal double category $_L\lCsp(\inta F)$ of structured cospans, where $L \maps \A \to \inta F$ is the left adjoint of the induced Grothendieck opfibration $U \maps \inta F \to \A$.
\end{thm}

@@

As noted for example by Shulman \cite{Shulman2010}, any double category $\lX$ has a 
\define{horizontal bicategory}, denoted $\bX$, in which:
\begin{itemize}
\item objects are objects of $\lX$,
\item morphisms are horizontal 1-cells of $\lX$,
\item 2-morphisms are \define{globular} 2-morphisms of $\lX$, meaning 2-morphisms whose source and target vertical 1-morphisms are identities,
\item composition of morphisms is given by horizontal composition of horizontal 1-cells in $\lX$,
\item vertical and horizontal composition of 2-morphisms are given by vertical and horizontal
composition of 2-morphisms in $\lX$.
\end{itemize}
The bicategory $\bX$ then has a \define{decategorification}, a category $\X$ in which:
\begin{itemize}
\item objects are objects of $\bX$,
\item morphisms are isomorphism classes of morphisms of $\bX$.   
\end{itemize}
Thus, the double category $F\lCsp$ of structured cospans constructed in \cref{thm:decorated_cospans} automatically gives rise to a bicategory, which we call $F\bCsp$, and a category, which we call $F\Csp$.   In \cref{DC} we gave conditions under which the double category $F\lCsp$ becomes symmetric monoidal.   We would like the bicategory $F\bCsp$ and the category $F\Csp$ to become symmetric monoidal under the same conditions, and indeed this is true.

A double category is `fibrant' if every vertical 1-morphism has a `companion' and a `conjoint'---concepts explained in \cref{def:companion}.   Shulman \cite[Thm.\ 1.2]{Shulman2010} showed how when a double category $\lX$ is fibrant, any symmetrical monoidal structure on $\lX$ gives one on $\bX$.     We can apply this to decorated cospans as follows:

@@

\begin{proof}
We show that any vertical 1-morphism $f \maps c \to c'$ in $F\lCsp$ has a companion and a conjoint.  This horizontal 1-cell $\hat{f}$:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$c$};
\node (B) at (1,0) {$c'$};
\node (C) at (2,0) {$c'$};
\node (D) at (1,-0.5) {$!_{c'} \in F(c')$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$f$} (B)
(C) edge node[above]{$1$} (B);
\end{tikzpicture}
\]
is a companion of $f$ because the following two 2-morphisms, having $\hat{f}$ as
source and target:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0.5) {$c$};
\node (A') at (0,-0.5) {$c'$};
\node (B) at (1,0.5) {$c'$};
\node (C) at (2,0.5) {$c'$};
\node (C') at (2,-0.5) {$c'$};
\node (D) at (1,-0.5) {$c'$};
\node (E) at (3,0.5) {$!_{c'} \in F(c')$};
\node (F) at (3,-0.5) {$!_{c'} \in F(c')$};
\node (G) at (5,0.5) {$c$};
\node (H) at (6,0.5) {$c$};
\node (I) at (7,0.5) {$c$};
\node (G') at (5,-0.5) {$c$};
\node (H') at (6,-0.5) {$c'$};
\node (I') at (7,-0.5) {$c'$};
\node (J) at (8,0.5) {$!_{c} \in F(c)$};
\node (K) at (8,-0.5) {$!_{c'} \in F(c')$};
\node (L) at (1,-1) {$\tau_{1_{c'}} = 1_{!_{c'}}$};
\node (M) at (6,-1) {$\tau_f \maps F(f)(!_c) \to !_{c'}$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$f$} (B)
(C) edge node[above]{$1$} (B)
(A) edge node[left]{$f$} (A')
(C) edge node[left]{$1$} (C')
(A') edge node[above] {$1$} (D)
(C') edge node[above] {$1$} (D)
(B) edge node [left] {$1$} (D)
(G) edge node [above] {$1$} (H)
(G) edge node [left] {$1$} (G')
(H) edge node [left] {$f$} (H')
(G') edge node [above] {$f$} (H')
(I) edge node [above] {$1$} (H)
(I) edge node [left] {$f$} (I')
(I') edge node [above] {$1$} (H');
\end{tikzpicture}
\]
satisfy the equations required of a companion:
\[
\begin{tikzpicture}[scale=1.5]
\node (N) at (0,1.5) {$c$};
\node (O) at (1,1.5) {$c$};
\node (P) at (2,1.5) {$c$};
\node (Q) at (-1,1.5) {$!_c \in F(c)$};
\node (A) at (0,0.5) {$c$};
\node (A') at (0,-0.5) {$c'$};
\node (B) at (1,0.5) {$c'$};
\node (C) at (2,0.5) {$c'$};
\node (C') at (2,-0.5) {$c'$};
\node (D) at (1,-0.5) {$c'$};
\node (E) at (-1,0.5) {$!_{c'} \in F(c')$};
\node (F) at (-1,-0.5) {$!_{c'} \in F(c')$};
\node (G) at (4,1) {$c$};
\node (H) at (5,1) {$c$};
\node (I) at (6,1) {$c$};
\node (G') at (4,0) {$c'$};
\node (H') at (5,0) {$c'$};
\node (I') at (6,0) {$c'$};
\node (J) at (7,1) {$!_{c} \in F(c)$};
\node (K) at (7,0) {$!_{c'} \in F(c')$};
\node (Q) at (1,-1) {$\tau_f \maps F(f)(!_c) \to !_{c'}$};
\node (L) at (1,-1.5) {$\tau_{c'} = 1_{!_{c'}}$};
\node (M) at (5,-0.5) {$\tau_f \maps F(f)(!_c) \to !_{c'}$};
\node (R) at (3,0.5) {$=$};
\path[->,font=\scriptsize,>=angle 90]
(N) edge node[above]{$1$} (O)
(P) edge node[above]{$1$} (O)
(N) edge node[left]{$1$} (A)
(O) edge node[left]{$f$} (B)
(P) edge node[left]{$f$} (C)
(A) edge node[above]{$f$} (B)
(C) edge node[above]{$1$} (B)
(A) edge node[left]{$f$} (A')
(C) edge node[left]{$1$} (C')
(A') edge node[above] {$1$} (D)
(C') edge node[above] {$1$} (D)
(B) edge node [left] {$1$} (D)
(G) edge node [above] {$1$} (H)
(G) edge node [left] {$f$} (G')
(H) edge node [left] {$f$} (H')
(G') edge node [above] {$1$} (H')
(I) edge node [above] {$1$} (H)
(I) edge node [left] {$f$} (I')
(I') edge node [above] {$1$} (H');
\end{tikzpicture}
\]
\[
\begin{tikzpicture}[scale=1.5]
\node (G) at (-1,0.5) {$c$};
\node (H) at (-1,-0.5)  {$c'$};
\node (I) at (-2,0.5) {$c$};
\node (J) at (-2,-0.5) {$c$};
\node (A) at (0,0.5) {$c$};
\node (A') at (0,-0.5) {$c'$};
\node (B) at (1,0.5) {$c'$};
\node (C) at (2,0.5) {$c'$};
\node (C') at (2,-0.5) {$c'$};
\node (D) at (1,-0.5) {$c'$};
\node (E) at (1,1) {$!_{c'} \in F(c')$};
\node (F) at (1,-1) {$!_{c'} \in F(c')$};

@@

(A) edge node[above]{$f$} (B)
(C) edge node[above]{$1$} (B)
(A) edge node[left]{$f$} (A')
(C) edge node[left]{$1$} (C')
(A') edge node[above] {$1$} (D)
(C') edge node[above] {$1$} (D)
(B) edge node [left] {$1$} (D)
(A) edge node[above]{$1$} (G)
(G) edge node[left]{$f$} (H)
(A') edge node[above]{$1$} (H)
(J) edge node[above] {$f$} (H)
(I) edge node[left] {$1$} (J)
(I) edge node [above] {$1$} (G);
\end{tikzpicture}
\]
and right hand sides of the above two equations are given respectively by the 2-morphisms $U_f$ and $1_{\hat{f}}$. The conjoint of $f$ is given by this horizontal 1-cell $\check{f}$, which is just the opposite of the companion above:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$c'$};
\node (B) at (1,0) {$c'$};
\node (C) at (2,0) {$c$};
\node (D) at (4,0) {$!_{c'} \in F(c')$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$1$} (B)
(C) edge node[above]{$f$} (B);
\end{tikzpicture}
\]
Just as $\hat{f}$ obeys the equations required of a companion, $\check{f}$ obeys the equations required of a conjoint.
\end{proof}

@@

This symmetric monoidal bicategory $F\bCsp$ is a superior version of the one constructed earlier by the second author \cite{Courser}, in that there is greater flexibility in the allowed 2-morphisms.    We can decategorify $F\bCsp$ to obtain a symmetric monoidal category generalizing the kind considered by Fong \cite{Fong}:

@@

In \cref{thm:equiv} we gave conditions under which the symmetric monoidal double category of \emph{decorated} cospans $F\lCsp$ is equivalent to the  symmetric monoidal double category of \emph{structured} cospans ${}_L \lCsp(\int F)$.   We now show that under the same conditions we get an equivalence of symmetric monoidal bicategories, and of categories.

\begin{thm} \label{thm:bicat_equiv}
Suppose $\ca{A}$ has finite colimits and $F \maps(\ca{A},+) \to (\bicat{Cat},\times)$ is a symmetric lax monoidal pseudofunctor that factors through $\bicat{Rex}$ as an ordinary pseudofunctor.    Define the symmetric monoidal bicategory $_L\bCsp(\inta F)$ as in \cref{thm:equiv}.   Then there is an equivalence of symmetric monoidal bicategories
\[      F\bCsp \simeq {}_L \bCsp(\inta F)   \]
of symmetric monoidal categories
\[      F\Csp \simeq {}_L \Csp(\inta F)  . \]
\end{thm}

\begin{proof} Hansen and Shulman \cite{HS} showed that the passage from symmetric monoidal double categories to symmetric monoidal bicategories is  functorial in a suitable sense, implying
that an equivalence of symmetric monoidal double categories $\lX \simeq \lY$ gives an equivalence of symmetric monoidal bicategories $\bX \simeq \bY$.    Since the process of decategorifying a bicategory merely discards 2-morphisms and takes isomorphism classes of 1-morphisms, the equivalence of symmetric monoidal bicategories $\bX \simeq \bY$ in turn induces an equivalence of symmetric monoidal categories $\X \simeq \Y$.   Thus, the theorem follows from \cref{thm:equiv}. \end{proof}

CHECK THAT OUR SORT OF EQUIVALENCE OF SYMMETRIC MONOIDAL DOUBLE CATEGORIES IS REALLY THAT USED BY HANSEN AND SHULMAN!!!
